---
title: "Case study"
author: 'Zahra Ahmadpour'
date: "13/8/2022"
output:
  html_document: default
  word_document: default
---



### Load the dataset and clean the data e.g. day and month:

```{r}
pacman::p_load(modelr,lubridate,DT,tidyr,stringr,tidyverse,lubridate,gutenbergr,
               caret,mlbench,inspectdf,readr,nycflights13,moments, 
               correlation,Hmisc,car, forecast,knitr)
melbourne  <- read_csv (file ='F:/melbourne.csv')


melbourne <- melbourne %>% mutate(month= factor(month(melbourne$Date)))
melbourne <- melbourne %>% mutate(week_day=factor(wday(melbourne$Date)))
melbourne <- melbourne %>% select(Date,`Evaporation (mm)` ,week_day,month,
                `Maximum Temperature (Deg C)`, `Minimum temperature (Deg C)`,
                `9am relative humidity (%)`)
head(melbourne)
```


### Univariate analysis:

To check the continuous variables have a skew that could be resolved by a log transform,first I will produce the histogram for each continuous variables and skewness of them then I will review the logarithm transformation if it is needed.

#### 1. Evaporation (mm):
  
```{r}
ggplot(melbourne,aes(x=`Evaporation (mm)`))+geom_histogram(col="black")
summary(melbourne$`Evaporation (mm)`)
skewness(melbourne$`Evaporation (mm)`,na.rm=TRUE)


# the log transformation of evaporation:
melbourne <- mutate(melbourne, log_eva=log(`Evaporation (mm)`))
ggplot(melbourne,aes(x=log_eva))+geom_histogram(col="black")+
   labs( x="log(`Evaporation (mm)`)")
melbourne$log_eva <- str_replace(melbourne$log_eva,"-Inf","NA")
melbourne$log_eva  <- as.numeric(melbourne$log_eva)

summary(melbourne$log_eva)
skewness(melbourne$log_eva,na.rm=TRUE)

```

#### 2. Maximum Temperature (Deg C):

```{r}
ggplot(melbourne,aes(x=`Maximum Temperature (Deg C)`))+geom_histogram(col="black")
summary(melbourne$`Maximum Temperature (Deg C)`)
skewness(melbourne$`Maximum Temperature (Deg C)`)

# log transformation of maximum Temperature:
melbourne <- mutate(melbourne,log_maxtemp=log(`Maximum Temperature (Deg C)`))
ggplot(melbourne,aes(x=log_maxtemp))+geom_histogram(col="black")+
  labs( x="log(`Maximum temperature (Deg C)`)")
summary(melbourne$log_maxtemp)
skewness(melbourne$log_maxtemp)
```

#### 3. Minimum temperature (Deg C):

```{r}
ggplot(melbourne,aes(x=`Minimum temperature (Deg C)`))+geom_histogram(col="black")
summary(melbourne$`Minimum temperature (Deg C)`)
skewness(melbourne$`Minimum temperature (Deg C)`)
```

#### 4. 9am relative humidity (%):

```{r}
ggplot(melbourne,aes(x=`9am relative humidity (%)`))+geom_histogram(col="black")
summary(melbourne$`9am relative humidity (%)`)
skewness(melbourne$`9am relative humidity (%)`)
```

### Bivariate analysis:

#### 1. log(`Evaporation (mm)`) vs. month:

```{r}
ggplot(melbourne,aes(x=log_eva, fill= month))+geom_histogram(col="black")+
   labs(x="log(`Evaporation (mm)`)")
ggplot(melbourne,aes(x=log_eva, fill= month))+
  geom_histogram(col="black")+facet_wrap(~month)+
  labs( x="log(`Evaporation (mm)`)")
ggplot(melbourne,aes(month,log_eva))+geom_boxplot()+
  labs( y="log(`Evaporation (mm)`)")
summary(melbourne$log_eva,melbourne$month)
res1 <- rcorr(melbourne$log_eva,melbourne$month)
res1$r
```

#### 2. log(`Evaporation (mm)`) vs. day of week:

```{r}
ggplot(melbourne,aes(x=log_eva, fill= week_day))+ geom_histogram(col="black")+
  labs(x="log(`Evaporation (mm)`)")
ggplot(melbourne,aes(x=log_eva, fill= week_day))+
  geom_histogram(col="black")+facet_wrap (~week_day)+
  labs(x="log(`Evaporation (mm)`)")
ggplot(melbourne,aes(week_day,log_eva))+geom_boxplot()+
  labs(y="log(`Evaporation (mm)`)")
summary(melbourne$log_eva,melbourne$week_day)
res2 <- rcorr(melbourne$log_eva,melbourne$week_day)
res2$r
```

#### 3. log(`Evaporation (mm)`) vs. log(`Maximum temperature (Deg C)`):

```{r}
ggplot(melbourne,aes(log_maxtemp,log_eva))+geom_point()+geom_smooth()+
  labs(x="log(`Maximum temperature (Deg C)`)",y="log(`Evaporation (mm)`)")

cor.test(melbourne$log_eva, melbourne$log_maxtemp)
```

#### 4. log(`Evaporation (mm)`) vs. `Minimum Temperature (Deg C)`:

```{r}
ggplot(melbourne,aes(`Minimum temperature (Deg C)`,log_eva))+geom_point()+geom_smooth()+
  labs(y="log(`Evaporation (mm)`)")

cor.test(melbourne$log_eva,melbourne$`Minimum temperature (Deg C)`)
```

#### 5. log(`Evaporation (mm)`) vs. `9am relative humidity (%)`:

```{r}
ggplot(melbourne,aes(`9am relative humidity (%)`,log_eva))+geom_point()+geom_smooth()+
   labs(y="log(`Evaporation (mm)`)")

cor.test(melbourne$log_eva,melbourne$`9am relative humidity (%)`)
```

### Check the independence of predictors:

```{r}
res <- rcorr(as.matrix(melbourne[,2:9]))
res$r
```

### Model Selection:

```{r}
melbourne$mintemp <- melbourne$`Minimum temperature (Deg C)`
melbourne$humid <- melbourne$`9am relative humidity (%)`
melbourne_lm1 <-lm (log_eva ~ week_day + month + log_maxtemp + mintemp + humid +  month:humid, data= melbourne)
summary(melbourne_lm1)
anova(melbourne_lm1)

# The model after removing the log maximum temperature:
melbourne_lm2 <- lm (log_eva ~ week_day + month + mintemp + humid + month:humid, data= melbourne)
summary(melbourne_lm2) 
anova(melbourne_lm2)

# Compare the both models by ANOVA:
anova(melbourne_lm1 , melbourne_lm2)

# Final model after removing the log maximum temperature and day of the week:
melbourne_lm3 <- lm (log_eva ~ month  + mintemp + humid + month:humid, data= melbourne)
summary(melbourne_lm3) 
anova(melbourne_lm3)



# Compare the both models by ANOVA:
anova(melbourne_lm2 , melbourne_lm3)
```

#### Check the model for interaction term:

```{r}
melbourne_lm4 <- lm (log_eva ~ month  + mintemp + humid , data= melbourne)
summary(melbourne_lm4)
anova(melbourne_lm4)

# Compare the both models by ANOVA:
anova(melbourne_lm4 ,melbourne_lm3)


```
 
### Model diagnostics (assumptions):

```{r}
# first assumption: check the linear model,
plot(melbourne_lm3,which=1)

# second assumption: check the homoscedasticity,
plot(melbourne_lm3,which=3)

# Third assumption: check the normality,
plot(melbourne_lm3,which=2)

# Forth assumption: check the Independence of observations,
checkresiduals(melbourne_lm3)

library(car)
durbinWatsonTest(melbourne_lm3)

# Outliers and high levarage points and Influential values,
plot(melbourne_lm3,which=4)
plot(melbourne_lm3,which=5)

library(broom)
model.diag.metrics <- augment(melbourne_lm3)
model.diag.metrics %>%
  top_n(3, wt = .cooksd)
```


### Predictions

. February 29, 2020, if this day has a minimum temperature of 13.8 degrees and reaches a
maximum of 23.2 degrees, and has 74% humidity at 9am.

. December 25, 2020, if this day has a minimum temperature of 16.4 degrees and reaches a
maximum of 31.9 degrees, and has 57% humidity at 9am.

. January 13, 2020, if this day has a minimum temperature of 26.5 degrees and reaches a
maximum of 44.3 degrees, and has 35% humidity at 9am.

. July 6, 2020, if this day has a minimum temperature of 6.8 degrees and reaches a maximum of 10.6 degrees, and has 76% humidity at 9am.


```{r}

pacman::p_load(mlbench)

feb_eva <- tbl_df(exp(predict(melbourne_lm3,newdata= tibble(month="2", mintemp=13.8, humid=74),interval="confidence")))

dec_eva <- tbl_df(exp(predict(melbourne_lm3,newdata= tibble(month="12", mintemp=16.4, humid=57),interval="confidence")))

jan_eva <- tbl_df(exp(predict(melbourne_lm3,newdata= tibble(month="1", mintemp=26.5, humid=57),interval="confidence")))

jul_eva <- tbl_df(exp(predict(melbourne_lm3,newdata= tibble(month="7", mintemp=6.8, humid=76),interval="confidence")))

tibble_lm1 <- tibble(month=c(1,2,7,12),
             fit=c(jan_eva$fit,feb_eva$fit,jul_eva$fit,dec_eva$fit),
             lwr=c(jan_eva$lwr,feb_eva$lwr,jul_eva$lwr,dec_eva$lwr),
             upr=c(jan_eva$upr,feb_eva$upr,jul_eva$upr,dec_eva$upr),
             range=c((jan_eva$upr-jan_eva$lwr),(feb_eva$upr-feb_eva$lwr),(jul_eva$upr-jul_eva$lwr),(dec_eva$upr-dec_eva$lwr)))
tibble_lm1 %>% head() %>%
  kable(caption = "**Table 1 Predictions of Evaporation(mm) with 95% confidence intervals.**", digits=2)

```

### The end

